Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
Removed comment
Changes to meth and comment in discussion

%Consider adding subsub for code+doc and interviews later
\subsection{Data Collection} \label{data_collection}
%Intro to code inspection
The data were collected primarily through inspections of the source code and the archival analysis of accompanying  documentation. The source code was comprised of two versions of an API which the company had developed. An older version (1.4) which is currently released and a newer version which has recently been deployed (2.0). Each version of the API had its own respective documentation. The documentation was inspected and organised to find explanations of the features offered by the API.

@@

The APIs were inspected to determine where the changes had occurred. We used the Git Diff tool to find differences between two versions of files that existed in both versions of the API. Once we had identified the changes, we inspected the documentation and the code itself to determine if there was a reason for the change, for example, if a given function had been labelled deprecated between versions. These changes were then categorised by new changes, updates or re-implementations, removals and general trends. The collected data were input into tables and spreadsheets, according to the API version.

@@

%Interviews !!!improve later
After the initial source code inspection had been performed, interviews were conducted. The main purpose of these was to validate our findings during the code inspection with the designers of the APIs. Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection. The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.

@@

%Description of code analysis
More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to. The data were then mapped and coded to the laws presented by \cite{lehman1980programs}. The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes. The final step involved analysis of these trends and it was during this stage the hypotheses were generated and formulated. The same approach taken to reduce risks of research bias and human error in the data collection was performed during results analysis.

@@

%Save this for conclusion? Or leave it here?
%While out of the scope of our research, it might be interesting to investigate if this trend occurs in other platform specific APIs.

@@

>>>>

%Consider adding subsub for code+doc and interviews later
\subsection{Data Collection} \label{data_collection}
%Intro to code inspection
The data were collected primarily through inspections of the source code and the archival analysis of the accompanying documentation. The source code was comprised of two versions of an API which the company had developed. An older version, 1.4, which is currently released and a newer version, 2.0, which has recently been deployed. Each version of the API had its own respective documentation. The documentation was inspected and organised to find explanations of the features offered by the API.

@@

The APIs were inspected to determine where the changes had occurred. We used the Git Diff tool to find differences between two versions of files that existed in both versions of the API. Once we had identified the changes, we inspected the documentation and the code itself to determine if there was a reason for the change, for example, if a given function had been labelled deprecated between versions. Similar changes will be grouped together based on commonalities between them. (!!!reword nicely)

@@

%Interviews !!!improve later
After the initial source code inspection had been performed, interviews were conducted. The main purpose of the interviews was to validate our findings during the code inspection with the designers of the APIs. Furthermore, the interviews were conducted to provide additional insight into decisions and motives behind changes that might have been overlooked during the code inspection. The final reason for interviewing the designers of the APIs was to provide further insight of the users of the API and how their decisions, needs and requirements have affected the development of the API.

@@

%Description of code analysis
More specifically, the approach undertaken was divided into three steps where the changes were first categorised based by following the decision tree for types \cite{chapin2001types}. The changes were then mapped according to the laws presented by \cite{lehman1980programs}. The changes were then analysed from a high-level point of view, the main goal of which was to identify trends in the changes. The final step involved analysis of both the trends and the changes. During this stage the hypotheses were generated and formulated. The same approach was taken to reduce the risks of research bias and human error in the data collection was also performed during results analysis.

@@

@@

              Interesting that hardware did not drive change. Could be studied further in a new study to see if this applies to platform specific APIs in general?
